\section{Relevant Research and Publications}



\orderedouterlist{

\entrybig
{\textbf{TESS-Atlas}}
{In prep}
{Obtaining Bayesian PE fits and cataloging all TESS Objects of interest with a transit model.}
{}
\innerlist{
	\entrylabeled[--]{First Bayesian PE catalog for all TESS objects of interest.}
	\entrylabeled[--]{Also fitting for systems with data for single-transits, or multiple-planets.}
	\entrylabeled[--]{\github{dfm/tess-atlas}}
}


\entrybig
{\textbf{Bayesian Parameter Estimation Deep-followup for GW Events}}
{In prep}
{Devising and utilising a ``deep-followup'' Bayesian analyses method on GW candidates.}
{}
\innerlist{
    \entrylabeled[--]{Demonstrate the mathematical path to constrain a few dependent priors.}
    \entrylabeled[--]{Analysing GW events that ambiguous PE results.}
    \entrylabeled[--]{\github{avivajpeyi/deep\_gw\_pe\_followup}}
}



\entrybig
{\textbf{Measuring properties of AGN disks with gravitational waves}}
{Submitted to MNRAS}
{Constructed a stellar mass BH population model for BH merging in AGN disks.}
{\link{https://arxiv.org/abs/2111.03992}{arXiv:2111.03992}}
\innerlist{
	\entrylabeled[--]{Simulated two AGN black hole populations.}
	\entrylabeled[--]{Tested if population inference can distinguish populations.}
	\entrylabeled[--]{\github{avivajpeyi/agn\_phenomenological\_model}}
}


\entrybig
{\textbf{Bayesian Search for IMBHs in LIGO data}}
{Submitted to ApJL}
{Implemented and ran a Bayesian search for IMBH in O2 data.}
{\link{https://arxiv.org/abs/2107.12109}{arXiv:2107.12109}}
\innerlist{
	\entrylabeled[--]{Ran $\sim0.2$M Bayesian PE analyses, totaling 1.2M core-hours.}
	\entrylabeled[--]{In addition finding previously detected GW events, we discovered a few new GW candidates.}
	\entrylabeled[--]{\gitligo{avi.vajpeyi/bcr\_pipeline}}
}

\vspace*{10px}
A full list of short-author paper that I have contributed to can be found \textcolor{color-title}{\href{https://shorturl.at/dnIU1}{here}}.

}